\section{Project Scope}
\subsection{In-Scope}

\begin{itemize}

	\item User Registration and Authentication\\       
        - Users will be authenticated by the system.
        The emails and passwords will be verified too.
        
        \item Community Request Submission\\
        - Develop a feature for community members to submit requests for support, which will be curated and made visible to verified organizations.
        
	\item Organization Dashboard\\
        - Create a dashboard for organizations to manage their profiles, showcase achievements, list projects, and generate detailed reports for sponsors.
        
	\item Event Management\\
        - Provide tools for organizations to create, update, and manage events, including features for volunteers to view and participate in these events.
        
	\item Sponsor Interface\\
        - Design a user-friendly interface for sponsors to browse projects, receive detailed impact reports, and connect with suitable initiatives.
        
	\item Verification Processes\\
        - Implement processes to verify organizations and sponsors to ensure trust and legitimacy within the platform.
        
	\item Collaboration Tools\\
        - Enable organizations to collaborate with each other, share resources, and coordinate activities to achieve common goals.
        
	\item User Profiles and Achievements\\
        - Allow users to create and update profiles, and for organizations to highlight their achievements and impact.
 
        \item Search and Filter Functions\\
        - Implement robust search and filtering options for users to find relevant projects, events, and opportunities.

        \item Reporting System\\
        - Develop a comprehensive reporting system to generate detailed reports for sponsors, showcasing project impacts and future opportunities.

        \item Feedback Mechanism\\
        - Create a system for users to provide feedback on events and projects, helping improve future initiatives.
	
\end{itemize}

\newpage

\subsection{Out-Scope}

\begin{itemize}
        \item Financial Transactions Handling: The system will not handle any financial transactions directly. All payments and donations will be processed outside the platform through the listed payment methods of the organizations.
        \item Inventory Management: The system will not include detailed inventory management for the organizations or community members.
        \item Direct Fund Allocation: The platform will not be responsible for the direct allocation of funds to projects. Organizations will handle all financial aspects independently.
        \item Legal and Compliance Advisory: The platform will not provide legal or compliance advisory services to users or organizations.
        \item Personal Data Storage Beyond Platform Use: The system will not store personal data beyond what is necessary for the operation of the platform. All data will be managed according to privacy policies and regulations.
\end{itemize}