
\subsubsection*{ADMIN}
\begin{itemize}
\itemsep0em 
    \item Admin shall be able to login to the system
    \item Admin shall be able to change passwords of all user accounts
    \item Admin shall be able to Disable/Enable Account all user accounts
    \item Admin shall be able to Edit his Profile
    \item Admin shall be able to Manage Complaints of users
    \item Admin shall be able to manage post.
    \item Admin shall be able to approve posts uploaded by the requester
    \item Admin shall be able to update posts
    \item Admin shall be able to delete posts
    \item Admin shall be able to view posts
    \item Admin shall be able to view his main dashboard
    \item Admin shall be able to view dashboards of organizations
    \item Admin shall be able to delete user reviews
    \item Admin shall be able to edit events
    \item Admin shall be able to remove events
    \item Admin shall be able to remove donation goals
    \item Admin shall be able to disable collaborations within organizations
    \item Admin shall be able to edit volunteer's profiles
    \item Admin shall be able to edit organization's profiles
    \item Admin shall be able to edit sponsor's profiles
    \item Admin shall be able to change sponsor preferences 
    \item Admin shall be able to change organization preferences
    \item Admin shall be able to respond to user inquiries and support requests
    \item Admin shall be able to ensure compliance with legal and ethical standards
\end{itemize}
\newpage
\subsubsection*{REQUESTER}
\begin{itemize}
\itemsep0em 
    \item Requester shall be able to log in to the system.
    \item Requester shall be able to change their password.
    \item Requester shall be able to edit their profile.
    \item Requester shall be able to submit a new issue or request.
    \item Requester shall be able to update their submitted requests.
    \item Requester shall be able to delete their submitted requests.
    \item Requester shall be able to view the status of their requests.
    \item Requester shall be able to receive notifications about the status of their requests.
    \item Requester shall be able to view profiles of organizations addressing their requests.
    \item Requester shall be able to rate and review organizations after their request has been addressed.
    \item Requester shall be able to update their reviews of organizations.
    \item Requester shall be able to delete their reviews of organizations.
    \item Requester shall be able to view the history of their submitted requests.
    \item Requester shall be able to contact support for any issues with the system.
    \item Requester shall be able to receive email notifications for important updates and information.
\end{itemize}

\subsubsection*{VOLUNTEER}
\begin{itemize}
\itemsep0em 
    \item Volunteer shall be able to log in to the system.
    \item Volunteer shall be able to change their password.
    \item Volunteer shall be able to edit their profile.
    \item Volunteer shall be able to view available events.
    \item Volunteer shall be able to register for events.
    \item Volunteer shall be able to view details of events they are registered for.
    \item Volunteer shall be able to cancel their registration for events.
    \item Volunteer shall be able to view event posts and updates.
    \item Volunteer shall be able to receive notifications about event updates and changes.
    \item Volunteer shall be able to submit feedback for events they attended.
    \item Volunteer shall be able to update their feedback for events.
    \item Volunteer shall be able to delete their feedback for events.
    \item Volunteer shall be able to view profiles of organizations hosting events.
    \item Volunteer shall be able to see issues submitted by requesters.
    \item Volunteer shall be able to view and filter issues based on categories and urgency.
    \item Volunteer shall be able to receive email notifications for important updates and information.
    \item Volunteer shall be able to contact support for any issues with the system.
\end{itemize}

\subsubsection*{ORGANIZATION}
\begin{itemize}
\itemsep0em 
    \item Organization shall be able to log in to the system.
    \item Organization shall be able to change their password.
    \item Organization shall be able to edit their profile.
    \item Organization shall be able to submit and update their volunteering initiatives.
    \item Organization shall be able to create and manage events.
    \item Organization shall be able to update event details.
    \item Organization shall be able to cancel events.
    \item Organization shall be able to view and manage volunteer registrations.
    \item Organization shall be able to send notifications and updates to volunteers.
    \item Organization shall be able to post updates and announcements about events.
    \item Organization shall be able to receive and view feedback from volunteers.
    \item Organization shall be able to generate reports on event outcomes and volunteer participation.
    \item Organization shall be able to upload and update their achievements and project summaries.
    \item Organization shall be able to view and filter issues submitted by requesters.
    \item Organization shall be able to select and address issues based on their capacity and resources.
    \item Organization shall be able to connect and collaborate with other organizations.
    \item Organization shall be able to update their sponsorship needs and perks.
    \item Organization shall be able to view profiles of potential sponsors.
    \item Organization shall be able to send sponsorship requests.
    \item Organization shall be able to receive notifications for sponsorship approvals and updates.
    \item Organization shall be able to generate a report showcasing their profile, achievements, and projects.
    \item Organization shall be able to contact support for any issues with the system.
\end{itemize}

\subsubsection*{MODERATOR}
\begin{itemize}
\itemsep0em 
    \item Moderator shall be able to log in to the system.
    \item Moderator shall be able to change their password.
    \item Moderator shall be able to view and manage their profile.
    \item Moderator shall be able to view all user accounts.
    \item Moderator shall be able to disable or enable user accounts.
    \item Moderator shall be able to approve or reject new user registrations.
    \item Moderator shall be able to approve or reject organization registrations.
    \item Moderator shall be able to review and approve or reject submitted issues by requesters.
    \item Moderator shall be able to filter and categorize submitted issues.
    \item Moderator shall be able to review and approve or reject event submissions.
    \item Moderator shall be able to monitor and review event updates and cancellations.
    \item Moderator shall be able to monitor and review volunteer registrations for events.
    \item Moderator shall be able to review and manage feedback and reports from volunteers and organizations.
    \item Moderator shall be able to view and manage all announcements and updates posted by organizations.
    \item Moderator shall be able to send notifications and updates to users regarding system changes and updates.
    \item Moderator shall be able to generate reports on system usage and activity.
    \item Moderator shall be able to view and manage sponsorship requests and approvals.
    \item Moderator shall be able to ensure compliance with system policies and guidelines.
    \item Moderator shall be able to investigate and resolve user complaints and issues.
    \item Moderator shall be able to manage system content to ensure appropriateness and relevance.
    \item Moderator shall be able to view and manage collaboration requests between organizations.
    \item Moderator shall be able to monitor the overall health and performance of the system.
    \item Moderator shall be able to escalate technical issues to the support or development team.
    \item Moderator shall be able to conduct audits and reviews of user activity and system logs.
    \\
    \\
    \\
    \\\\\\
    \\
    \\
    \\
    \\
    \\
    \\
    \\
\end{itemize}


\clearpage